Equations & R Code

### 2016-06-06 manuscript/manuscript.Rmd
adds multi species version of model function

```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, fig.height=3, fig.width=5, fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (*a,b*) and relative nonlinearity (*c,d*) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their germination fractions are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their germination fractions are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
# mycols <- c("#9D6188","#97A861")
# mycols <- c("black", "grey")
mycols <- c("red", "blue")

>>>>

```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, fig.height=3, fig.width=5, fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (*a,b*) and relative nonlinearity (*c,d*) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their germination fractions are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their germination fractions are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
# mycols <- c("#9D6188","#97A861")
# mycols <- c("black", "grey")
mycols <- c("grey", "skyblue")
